A Formal Logic for Formal Category Theory

### 2022-10-14 paper/paper.tex
last part

\section{\vett{} Syntactic Metatheory}
\label{sec:appendix:syntax}

@@

\section{Extended Formal Category Theory Examples}
\label{sec:appendix:examples}

@@

\section{Semantics}
\label{sec:appendix:semantics}

@@

\begin{definition}[Syntactic Virtual Equipment]
  Fix a context $\Gamma$. Define a virtual equipment $\Syn^\Gamma$ as
  follows:
  \begin{enumerate}
  \item The vertical category $\Syn^\Gamma_o$ has categories $\Gamma
    \vdash \cat C \isaCat$ as objects, small categories as small
    objects and as arrows from $\cat C$ to $\cat D$ objects
    $\alpha:\cat C \vdash b : \cat D$ modulo renaming of the input
    variable. Composition is given by substitution and identity is the
    variable.
  \item The horizontal arrows are the sets $\alpha:\cat C; \beta:\cat
    D \vdash R$ up to renaming with source $\cat C$ and target $\cat
    D$.
  \item Note that composable strings $\vec R$ of horizontal arrows are
    in bijection with contexts $\Phi$. Then we can define a 2-cell
    $\Syn^\Gamma_2(\Phi, a, b, S)$ to be an element
    $\Gamma\pipe\Phi\vdash s : S[a/\alpha;b/\beta]$.

>>>>

\section{Details of \vett{} Syntax and Syntactic Metatheory}
\label{sec:appendix:syntax}

@@

\section{Details of Formal Category Theory Examples}
\label{sec:appendix:examples}

@@

\section{Details of Semantics}
\label{sec:appendix:semantics}

@@

\begin{definition}[Syntactic Virtual Equipment]
  Fix a context $\Gamma$. Define a virtual equipment $\Syn^\Gamma$ as
  follows:
  \begin{enumerate}
  \item The vertical category $\Syn^\Gamma_o$ has categories $\Gamma
    \vdash \cat C \isaCat$ as objects, small categories as small
    objects and as arrows from $\cat C$ to $\cat D$ objects
    $\alpha:\cat C \vdash b : \cat D$ modulo renaming of the input
    variable. Composition is given by substitution and identity is the
    variable.
  \item The horizontal arrows are the sets $\alpha:\cat C; \beta:\cat D
    \vdash R$ (up to renaming $\alpha$ and $\beta$) with source $\cat C$
    and target $\cat D$.
  \item Note that composable strings $\vec R$ of horizontal arrows are
    in bijection with contexts $\Phi$. Then we can define a 2-cell
    $\Syn^\Gamma_2(\Phi, a, b, S)$ to be an element
    $\Gamma\pipe\Phi\vdash s : S[a/\alpha;b/\beta]$.
